---
title: "Week 8 – Homework"
author: "Agnes Boel Nielsen"
date: "22/03/2022 updated`r Sys.Date()`"
output:
  rmdformats::readthedown:
    highlight: kate
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(spatstat)
```

# Exercise 1, Task 7: Point Pattern testing

Two `ppp` objects have been created called `p1` and `p2` in your /data folder. Test if they are clustered or regular, and select the right answer. You'll need to run `quadrat.test` four times, once for each process with each hypothesis.

### Possible Answers

1. p1 is regular, p2 is regular
2. p1 is regular, p2 is clustered 
3. **p1 is clustered, p2 is clustered** <-- This is the correct answer!
4. p1 is clustered, p2 is regular

```{r testing,eval= FALSE}
p1 <- readRDS("../data/p1.rds")
p2 <- readRDS("../data/p2.rds")

plot(p1)
plot(p2)

quadrat.test(p1, alternative = "clustered") # 0.02461
quadrat.test(p1, alternative = "regular") # 0.9754
quadrat.test(p2, alternative = "clustered") # 0.00062
quadrat.test(p2, alternative = "regular") # 0.9994
```

# Exercise 2, Task 3: Tree location pattern


Load a `ppp` object called `redoak` which contains the locations of trees in a woodland. Plot the tree locations and then test the hypothesis that the points are clustered against a *null hypothesis of a random uniform distribution*.

## Possible Answers

* I cannot reject the null hypothesis. 
* I can reject the null hypothesis with p-value less than 0.1 
* **I can reject the null hypothesis with p-value less than 0.01** <-- This is the answer! The p-value from the quadrat test is 4.477e-07, i.e. <0.01. 

### Hint: check out the measure from the first exercise 
```{r Tree location pattern}
# Load the object
redoak <- readRDS("../data/redoak.rds")

# Plot the tree locations
plot(redoak)

# Nearest neighbour
nnd_redoak <- nndist(redoak)

# Histogram
hist(nnd_redoak)

# Plot
G_redoak <- Gest(redoak)
plot(G_redoak)

# K-function
K_redoak <- Kest(redoak, correction = "border")

# Plot the K function with the default formula
plot(K_redoak, . ~ r)

# Plot the K function with a formula that subtracts the theoretical Poisson value
plot(K_redoak, . - pi * r ^ 2 ~ r)

# Simulation envelope with a formula that subtracts the theoretical Poisson value
K_redoak_env <- envelope(redoak, Kest, correction = "border")
plot(K_redoak_env, . - pi * r^2 ~ r)

# Quadrat test
quadrat.test(redoak, alternative = "clustered")
```