---
title: "05 - Raster manipulation"
author: "Agnes Boel Nielsen"
date: "06/02/2022 updated `r Sys.Date()`"
output:
  rmdformats::readthedown:
  highlight: kate
---


```{r setup, include=FALSE}
library(knitr)
library(rmdformats)

## Global options
options(max.print="75")
opts_chunk$set(echo=TRUE,
	             cache=TRUE,
               prompt=FALSE,
               tidy=TRUE,
               comment=NA,
               message=FALSE,
               warning=FALSE)
opts_knit$set(width=75)
```


```{r}
# Library
library(raster)
library(rgdal)
library(sf)
library(mapview)
```


# Task 7 - HOMEWORK: Inspect the most prominent mounds

In the above exercise, we produced an elevation-prominence overlay. Mounds and other sites that sit in this overlay enjoy a strategic position vis-a-vis the rest of the valley. Which ones are they, however, and what are their real prominence values?  It is hard to see at the scale of the valley and it would be good to pull the sites out. 

Find the mounds that enjoy the most prominent locations as well as those that feature in the elevation-prominence overlay raster. Produce a list of the ID numbers (TRAP_Code) of all the overlay mounds and 25 most prominent mounds and plot them (expressing their prominence somehow) . 

## Instructions

* Find or recreate the `mounds` sf object, `prominence` and `prom-el-overlay` rasters.
```{r}
# Recreate the `mounds` sf object, `prominence` and `prom-el-overlay` rasters (W5: Task 1-6)
elevation <- raster("../data/Aster.tif")
mounds <- st_read("../data/KAZ_mounds.shp")
prominence <- raster("../data/prominence1500m.tif")

vals <- getValues(elevation)
vals_recl <- cbind(-10000, 0, NA)
elevation_reclass <- reclassify(elevation, rcl = vals_recl)
elev <- raster::crop(elevation_reclass, mounds)

mounds$elev <- raster::extract(elevation, mounds)

f <- function(rast1, rast2) {
  rast1 > 400 &
  rast1 < 650 &
  rast2 > 60}

prominence <- raster::crop(prominence,elev_cropped)

prom_el_overlay <- overlay(elev, prominence, fun = "f")

```


* Plot the `prom-el-overlay` and the `mounds` on top of each other to check visual overlap. Do the same with `prominence` raster and `mounds`.
```{r}
# Plot the `prom-el-overlay` raster and the `mounds` on top of each other
plot(prom_el_overlay)
plot(mounds$geometry, add = TRUE)

# Plot the `prominence` raster and the `mounds` on top of each other
plot(prominence)
plot(mounds$geometry, add = TRUE)
```

* Extract values from the elevation-prominence overlay raster and from the prominence raster at mounds and write them to two columns:

  -- call the first column `prom_el_overlay` 
  -- name the second column `prominence` 
```{r}
# Extract values and write to columns
mounds$prom_el_overlay <- raster::extract(prom_el_overlay, mounds)
mounds$prominence <- raster::extract(prominence,mounds)
```


* Make an object of mounds that sit within these strategic high-visibility locations. How many are there?
```{r}
# Make an object of mounds that sit within these strategic high-visibility locations
mount_high_vis <- raster::crop(prom_el_overlay, mounds)
```

* Make an object of 25 mounds with the highest prominence values. Which `TRAP_Code` ids are included? - *2002, 3112, 3105, 4057, 4058, 3722, 4059, 3417, 4056, 3276, 3024, 1020, 4087, 1019, 3026, 2028, 4066, 5002, 4086, 1071, 3275, 2003, 2004, 3703, 3420.*
```{r}
# Make an object of 25 mounds with the highest prominence values
prom_25 <- mounds %>% 
  dplyr::arrange(desc(prominence)) %>%
  dplyr::slice(1:25)

prom_25$TRAP_Code
```


* Plot both these sets of mounds in `mapview()` and compare their locations. 
```{r prom-mnd-ex}
# Plot both these sets of mounds
plot(mount_high_vis)
plot(prom_25, add = TRUE)

# Plot with mapView
mapView(mount_high_vis) + 
  (prom_25)
```

### Question:

*5. How do the mounds with high prom_el_overlay values differ from those with high prominence? *
